Summer 2024 Report

### 2024-11-21 Relations/Report.tex
ars

\documentclass{scrartcl}
% \input{packages}
\input{macros}

@@

\begin{document}

@@

\section{Implications}
We now look into the interrelation of the various properties defined in Section~\ref{section:Definitions}. Our aim is to expand on the
connections made in Figure 1.8 of [TeReSe] (p.19).

@@

\texttt{i : WN R → UN R → bounded R}

@@

>>>>

\documentclass{scrartcl}
% \input{packages}

\usepackage{booktabs}

\input{macros}

@@

\begin{document}
\renewcommand{\arraystretch}{1.3}

@@

\section{Implications}
{\small
We now look into the interrelation of the various properties defined in Section~\ref{section:Definitions}. Our aim is to expand on the
connections made in Figure 1.8 of [TeReSe] (p.19).

@@

\texttt{i : WN R $\to$ UN R $\to$ bounded R}

@@

\end{itemize}
}

\subsection{Summary table}
BP = boundedness property

Table listing highest "confluence" property implied
by the conjunction of row and column.
\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
  \toprule
  CP & CR & WCR & WNFP & WUN \\
  \midrule
  SN  & & & & \\
  WN  & & & & \\
  WN*  & & & & \\
  BP $\land$ CP   & & & & \\
  BP  & & & & \\
  CP  & & & & \\
  \bottomrule
\end{tabular}

Table listing highest "normalization" property implied 
by the conjunction of row and column.
\begin{tabular}{@{}l@{\quad}l@{\quad}l@{\quad}l@{\quad}l@{}}
  \toprule
  CP & CR & WCR & WNFP & WUN \\
  \midrule
  SN  & & & & \\
  WN  & & & & \\
  WN*  & & & & \\
  BP $\land$ CP   & & & & \\
  BP  & & & & \\
  CP  & & & & \\
  \bottomrule
\end{tabular}
